---
title: "Nashrah_Ahmed_HW02"
author: "Nashrah Ahmed"
date: "October 1, 2017"
output: html_document
---

Question 1:
99 bottles of beer on the wall, 99 bottles of beer.
Take one down, pass it around, 98 bottles of beer on the wall...
No more bottles of beer on the wall, no more bottles of beer.
Go to the store and buy some more, 99 bottles of beer on the wall.
```{r}
#loop
n <- 99
beersong <-
if (n==1) {
    cat("\n",n," bottle of beer on the wall, ",n,
        " bottles of beer.\nTake one down and pass it around,",
        " no more bottles of beer on the wall.\n", sep="")
    cat("\nNo more bottles of beer on the wall, no more bottles of beer.\n",
        "Go to the store and buy some more, 99 bottles of beer on the wall.\n", sep="")
  } else {
    cat("\n",n," bottles of beer on the wall, ",n,
        " bottles of beer.\nTake one down and pass it around, ",
        n-1, " more bottles of beer on the wall.\n", sep="")
  }


#function 
beersong <- function(n) {
  if (n==1) {
    cat("\n",n," bottle of beer on the wall, ",n,
        " bottles of beer.\nTake one down and pass it around,",
        " no more bottles of beer on the wall.\n", sep="")
    cat("\nNo more bottles of beer on the wall, no more bottles of beer.\n",
        "Go to the store and buy some more, 99 bottles of beer on the wall.\n", sep="")
  } else {
    cat("\n",n," bottles of beer on the wall, ",n,
        " bottles of beer.\nTake one down and pass it around, ",
        n-1, " more bottles of beer on the wall.\n", sep="")
    return(beersong(n-1))
  }
}

#test for full song
beersong(99)

```

function (print 95:99)
```{r cars}
beersong1 <- function(n) {
  if (n==95) {
    cat("\n",n," bottles of beer on the wall, ",n,
        " bottles of beer.\nTake one down and pass it around, ",
        n-1, " more bottles of beer on the wall.\n", sep="")
  } else {
    cat("\n",n," bottles of beer on the wall, ",n,
        " bottles of beer.\nTake one down and pass it around, ",
        n-1, " more bottles of beer on the wall.\n", sep="")
    return(beersong1(n-1))
  }
}

beersong1(99)

```

plot loop without function
``````{r}
n <- 10
plot <- {
    plot(1, type="n", xlab="x", ylab="y", xlim = c(0, n+1), ylim = c(0, n+1))
    for (i in 0:n) {
      segments(0,i,10,i)
      segments(i,0,i,0)
      points(i,i)
    }
}  

```

plot loop with function
```{r}
plot_f <- function(n=10) {
    plot(1, type="n", xlab="x", ylab="y", xlim = c(0, n+1), ylim = c(0, n+1))
    for (i in 0:n) {
      segments(0,i,10,i)
      segments(i,0,i,0)
      points(i,i)
    }
}  

plot_f()
```

individual stat functions
```{r}
df <- data.frame(
  a = c(5, 10, 15, 20))

output <- vector("double", ncol(df))
output

for (i in seq_along(df)) {            
 output[1] <- mean(df[[1]])
}
output[1]

col_mean <- function(df) {
  for (i in seq_along(df)) {
  output[1] <- mean(df[[1]])
  }
  output
}
col_mean(df)

col_median <- function(df) {
  for (i in seq_along(df)) {
  output[1] <- median(df[[1]])
  }
  output
}
col_median(df)

col_max <- function(df) {
  for (i in seq_along(df)) {
  output[1] <- max(df[[1]])
  }
  output
}
col_max(df)

col_min <- function(df) {
  for (i in seq_along(df)) {
  output[1] <- min(df[[1]])
  }
  output
}
col_min(df)

```

general function for desc stats
```{r}
col_summary <- function(df, stat) {
  output <- vector("numeric", length(df))
  for (i in seq_along(df)) {
    output[1] <- stat(df[[1]])
  }
  output
}

col_summary(df, stat = min)
col_summary(df, stat = max)
col_summary(df, stat = median)

```

```{r}
#error #1: empty vector
df_error <- data.frame(
  a = c())

col_summary_error <- function(df_error, stat) {
  output <- vector("numeric", length(df_error))
  for (i in seq_along(df_error)) {
    output[1] <- stat(df_error[[1]])
  }
  output
}

col_summary_error(df_error, stat = max)
```

```{r}
#error #2: NAs
df_error1 <- data.frame(
  b = letters[1:5])

col_summary_error1 <- function(df_error1, stat) {
  output <- vector("numeric", length(df_error1))
  for (i in seq_along(df_error1)) {
    output[1] <- stat(df_error1[[1]])
  }
  output
}

print(col_summary_error1(df_error1, stat = mean))

```

```{r}
#stop if vector is empty or contains NAs
col_summary_error2 <- function(vector, stat) {
  if(length(vector) == 0) {
    return('no values')}
  if(all(is.na(vector))) {
    return('has NAs')}
}
vector <- c(NA, NA, NA)
col_summary_error2(vector)

```

```{r}
vector1 <- c()
col_summary_error2(vector1)
```